\documentclass[11pt]{article}

% Change "review" to "final" to generate the final (sometimes called camera-ready) version.
% Change to "preprint" to generate a non-anonymous version with page numbers.
\usepackage[preprint]{acl}

% Standard package includes
\usepackage{times}
\usepackage{latexsym}

% For proper rendering and hyphenation of words containing Latin characters (including in bib files)
\usepackage[T1]{fontenc}

% This assumes your files are encoded as UTF8
\usepackage[utf8]{inputenc}

% This is not strictly necessary, and may be commented out,
% but it will improve the layout of the manuscript,
% and will typically save some space.
\usepackage{microtype}

% This is also not strictly necessary, and may be commented out.
% However, it will improve the aesthetics of text in
% the typewriter font.
\usepackage{inconsolata}

% Additional packages
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{pifont}
\usepackage{multirow}
\usepackage{stfloats}

% If the title and author information does not fit in the area allocated, uncomment the following
%\setlength\titlebox{<dim>}

\author{
 \textbf{Bingxi Zhao\textsuperscript{1,2}$^*$},
 \textbf{Jiahao Zhang\textsuperscript{1}$^*$},
 \textbf{Xubin Ren\textsuperscript{1}},
 \textbf{Zirui Guo\textsuperscript{1}},
 \textbf{Chao Huang\textsuperscript{1}$^\dagger$}
\\
 \textsuperscript{1}University of Hong Kong,
 \textsuperscript{2}Beijing Jiaotong University,
\\
 \small{
   \textbf{Correspondence: \{bingxizhao39, chaohuang75\}@gmail.com} 
 }
}

\begin{document}
\title{DeepTutor: Tool-Augmented Personalized Tutoring System}
\maketitle

\begin{abstract}
\renewcommand{\thefootnote}{}%
\footnotetext{\hspace{-1.8em}$^*$Equal contribution.\newline $^\dagger$Corresponding author.}%
\renewcommand{\thefootnote}{\arabic{footnote}}%
\setcounter{footnote}{0}%
Education is one of the most promising real-world applications for Large Language Models (LLMs). However, current LLMs rely heavily on static knowledge from pre-training, and existing Retrieval-Augmented Generation (RAG) systems often prioritize retrieval precision over the adaptive, guided explanations essential for effective tutoring. 
In this paper, we present \textsc{DeepTutor}, a fully open-source agentic framework that unifies citation-grounded problem-solving with difficulty-calibrated question generation. 
These capabilities are integrated through a hybrid personalization engine that couples static knowledge grounding with a trace forest, which continuously refines evolving learner profiles to customize every interaction. 
To evaluate personalized tutoring, we construct TutorBench, featuring 100 KB-grounded customized learner profiles. 
We further conduct interactive assessments via a profile-driven student simulator, complemented by general problem-solving evaluations on authoritative benchmarks. 
Our results demonstrate that \textsc{DeepTutor} excels in personalized scenarios while maintaining robust generalized agentic abilities. 
The \textsc{DeepTutor} system and its evaluation suites are open-sourced at \url{https://github.com/HKUDS/DeepTutor}.
\end{abstract}

% ===== Sections =====
\input{sections/intro}
\input{sections/related-work}
\input{sections/method}
\input{sections/experiments}
\input{sections/conclusion}
\input{sections/limitation}

\section*{Acknowledgments}

% Bibliography
\bibliography{custom}

\appendix
\input{sections/appendix}

\end{document}
